% arara: xelatex
% arara: make: { task: "cv.png" }
\documentclass{simplecv}
\BetterSetup{
  textout = \jobname.cv.txt,
  textout-preamble = preamble.txt,
}
%\CensorInformation

\usepackage{additional-setup}
\usepackage{ragged2e}

\ContactInformation{
    name   = Arun Lakshmanan,
    email  = lakshma2@illinois.edu,
    url    = www.arunlakshmanan.com,
    phone  = 217\,979\,5708,
    street = 210 E White Apt 3,
    city   = Champaign,
    state  = Illinois,
    zip    = 61820,
}

\newif\ifmath
\newif\ifgithub
\newif\ifinterests

\IfCensoredTF{}{\IfFileExists{./contact-info.tex}{\input{contact-info}}{}}

\mathtrue
\githubtrue
\intereststrue

\begin{document}
\maketitle
\vfill
\section{Technical Summary}
\begin{minipage}{\textwidth}
\begin{description}
\item[Languages]
    Python,
    C,
    \CPP,
    \CSharp,
    Bash,
    \TeX

\item[Libraries]
    NumPy,
    SciPy,
    Matplotlib,
    PSOPT,
    scikit-learn,
    opencv 

\item[Software]
    MATLAB,
  \software{Simulink},
  \software{\cli{git}},
  Processing,
  Unity

\item[Operating Systems]
    Linux (Ubuntu),
    ROS (Indigo)
\item[Hardware]
    mbed LPC1768,
    Odroid XU4,
    Beaglebone Black,
    AutoQuad 6,
    CrazyFlie 2.0
\end{description}
\end{minipage}

\vfill
\section{Education and Academic Experience}
\begin{education}
  {
      major = \textbf{Aerospace Engineering},
      degree = Master of Science,
      school = University of Illinois at Urbana-Champaign,
      school-link = http://www.ae.illinois.edu/,
      state = IL,
      city = Urbana,
      date = 2014 - \textit{expected} 2016,
  }

\begin{description}
    \item[Relevant Coursework]
        \course{Advanced Robotics Planning},
    \course{Nonlinear \& Adaptive Control},
    \course{Virtual Reality},
    \course{Control System Theory \& Design},
    \course{Introduction to Robotics},
    and \course{Digital Control Systems}
\item[Research] Working with \censor{Prof.~Naira~Hovakimyan} in optimal trajectory generation for robotic agents in urban environments.
  
\end{description}
\end{education}
\begin{education}
  {
      major = \textbf{Mechanical Engineering},
      degree = Bachelor of Technology,
      school = VIT University,
      school-link = http://www.vit.ac.in/,
      state = India,
      city = Vellore,
      date = 2010 - 2014,
  }

\begin{description}
    \item[Relevant Coursework]
    \course{Numerical Methods},
    \course{Finite Element Analysis},
    \course{Dynamics of Machinery},
    and
    \course{Computational Fluid Dynamics}
\item[Research] Worked under \censor{Prof.~Satyajit~Ghosh} on modeling accreted ice on aircraft structures for light passenger aircrafts.
\item[Abroad] 
    Worked at the \href{http://www.stratch.ac.uk/engineering}{\censor{University of Stratclyde}} in \censor{Scotland} on space-related projects and participated at the Scottish Space School. \censor{(Jun 2012)}
\end{description}
\end{education}

\begin{position}
  {
      print   = true,
      title   = Research Assistant,
      date    = Summer 2015 - (Current),
      company = UIUC
  }

  \begin{itemize}
      \item Optimal trajectory generation for robots in congested environments.
      \item Integration of quadrotors in public safety applications.
  \end{itemize}
\end{position}

\begin{position}
  {
      print   = true,
      title   = Teaching Assistant,
      date    = Spring 2015,
      company = UIUC
  }

  \begin{itemize}
      \item Taught a course on numerical methods in the Computer Science department.
      \item Mentored students on different numerical analysis methods and their implementation in \textit{Python}.
  \end{itemize}
\end{position}

\section{Research Experience}

\begin{position}
  {
    title   = Software Developer,
    company = Epic Systems Corporation,
    company-link = http://www.epic.com,
    date    = Jan 2015-*,
    city    = Verona,
    state   = WI,
    technical,
  }

\begin{itemize}
\item To be determined\dots
\end{itemize}
\end{position}

\begin{position}
  {
    title   = Junior Software Dev.,
    company = General Dynamics,
    company-link = http://www.gd-ais.com,
    date    = June 2014-Jan 2015,
    city    = Fairfax,
    state   = VA,
    technical,
  }

\begin{itemize}
\item Maintained and enhanced existing software solution using X~programming.
\item Redesigned graphical system to adhere to best practices in object-orientism.
\item Consolidated duplicated functionality and polished an NFS mount manager.
\end{itemize}
\end{position}

\begin{position}
  {
    title   = Server Administrator,
    company = St. Mary's College,
    company-link = http://www.smcm.edu/mathcs,
    date    = Sept 2013-May 2014,
    city    = St. Mary's City,
    state   = MD,
    technical,
  }

\begin{itemize}
\item Prepared and implemented an authenticated documentation server using \href{http://www.redmine.org}{Redmine}.
\item Maintained the hardware, software, firewalls, and other security measures
  for the department's subnetwork of 10\,--\,15 servers (both physical and virtual) via remote Linux administration using \texttt{ssh}\slash PuTTY.
\end{itemize}
\end{position}

\begin{position}
  {
    title   = Intern,
    company = {Progeny Systems, Inc.},
    company-link = http://progeny.net,
    date    = May-Sept 2013,
    city    = California,
    state   = MD,
    technical,
  }

\begin{itemize}
\item Created, documented, and maintained several virtual systems
  and virtualized existing infrastructure systems with vSphere\slash KVM via primarily remote Linux administration.
%\item Generated a skeleton graphical interface to a \textsc{cli} (YASCA) with Java.
\item Independently responded to and resolved non-critical emergency situations swiftly
  with minimal down-time or impact to end-users.
%\item Acquired expository experience for a range of topics including
%  networks,
%  databases,
%  server setup, and
%  remote administration.
\end{itemize}
\end{position}

\begin{position}
  {
    title   = Student Technician,
    company = St. Mary's College,% \Dash Office of Information Technology,
    company-link = http://oit.smcm.edu,
    city    = St. Mary's,
    state   = MD,
    date    = 2010-2013,
  }

\begin{itemize}
\item Supported clients in the use of the network and their software,
  troubleshooting both software and hardware problems on both Windows (Dell) and Apple computers.
\item Inventoried and organized departmental property.
\item Prepared aged hardware for release within state security specifications.
\end{itemize}
\end{position}

\begin{position}
  {
    title   = Software Developer,
    company = Capital Women's Care,
    company-link = http://www.cwcare.net,
    city    = Silver Spring,
    state   = MD,
    date    = 2008-2011,
    print   = false,
    technical,
  }

\begin{itemize}
\item Formalized and removed ambiguities to establish and document project scope.
\item Developed and maintained several \CSharp\,.NET applications to
  improve hiring workflow for multiple offices in the tri-state area.
  \item Yolo
  \item soflo
\end{itemize}
\end{position}

\vfill \vfill
\newpage

\section{Personal Information \& Interests}
\begin{itemize}
\item Experienced user of \LaTeX, a system used to produce documents
  of high quality and typographical consistency.
\item Currently an official representative of
  \href{http://meta.tex.stackexchange.com/a/4174/17423}{StackExchange}
  to the international \href{http://www.tug.org}{\TeX\ User's Group}.
\item Contributed \TeX\ extension packages to CTAN.
\item Edited and produced a promotional video for a \href{http://www.smcm.edu/desousabrent}{diversity program} at \censor{St. Mary's College} (archived).
\item Maintain\slash contribute to several
  \href{http://www.github.com/vermiculus}{open-source projects}
  using more conventional languages, such as
  \software{Emacs}~\Lisp, Python, Java, C, and Objective~C.
  (Contributions range from testing to discussion to design to program code.)
\end{itemize}

\renewcommand\refname{Publications}
\begin{thebibliography}{9}

    \bibitem{IEEEVR} 
    Marinho, Lakshmanan, Cichella, Widdowson, Cui, Jones, Sebastian, Goudeseune. 
    \textbf{VR Study of Human-Multicopter Interaction in a Residential Setting}. 
    \textit{Virtual Reality (VR), IEEE}. IEEE, 2016.

    \bibitem{IEEEVR} 
    Lele, Lakshmanan. 
    \textbf{Optimization of Extreme-Weather Forecasting Systems in Developing Nations}.
    \textit{International Research Journal of Earth Sciences}, 2015.
\end{thebibliography}
        
\section{Awards}
\begin{itemize}
    \item Twice CSL Video of the Month award winner at University of Illinois.
    \item Winner of 
\end{itemize}
\ifinterests
\vfill

\centering
Additional details on my projects and interests can be found at
\url{www.arunlakshmanan.com}.
\fi
\vfill
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% TeX-PDF-mode: t
%%% TeX-command-default: "arara"
%%% TeX-engine: xetex
%%% End:

%  LocalWords:  gpa adraig Jamieson Mathematica Powerpoint OneNote
%  LocalWords:  JSON cli YASCA Camtasia tri PDF PostgreSQL Visio CTAN
%  LocalWords:  Visio Redmine company-link title-link StackExchange
%  LocalWords:  StackMode ghkey vermiculus
